---
title: "plsr_neon_plot_traits"
author: "Sarah Graves"
date: "June 23, 2016"
output: html_document
---

# Goal  

Use PLS regression to relate foliar nitrogen (plot level kg/ha) to remote sensing data.

## PLSR model

Decided to use the `PLS` package because it was cited in this paper: http://onlinelibrary.wiley.com/doi/10.1890/13-2110.1/full

```{r LOAD PACKAGES}

library(pls)

# load sample data

data("gasoline")

```


# Use Kunxuan's code to create spectra for each plot

Waiting for updated code to generate plot-level spectra.
In the mean time, I am creating a dataframe with dummy data to test the PLSR

```{r}

# need Leah's code
library(raster)
library(rhdf5)
library(neonAOP)

f <- "../NEONdata/D03-Florida/OSBS/2014/spectrometer/reflectance/Subset1NIS1_20140507_150703_atmcor.h5"

bands <- c(1:426)

# create stack from all bands
# this takes a few minutes to run
hs <- create_stack(f,bands=bands,epsg=epsg)

# pull out pixels to use
# this is just the first 100 pixels (the first 100 cols in the first row)
hs_refl <- hs[1:100,1,1]

# calculate mean spectra for all pixels in raster stack
hs_mean <- extract_av_refl(hs,aFun=mean)

# remove bad bands
aop_bands <- read.csv("supplemental_data/neon_aop_bands.csv")

hs_mean[aop_bands$noise == 1] <- NA

plot(hs_mean)

```

## N content data

I will use plot-level kg of N. I am waiting for Jeff to get this? I can also work on it.
For now, I will create fake N data. Because I only have 1 plot, I will create fake N data for all pixels in the h5 clip.

```{r N-DATA}

# how many "plots" do I have?
# use the first row of the hs data
dim(hs_refl)

# fake N data
n_kg <- round(runif(n=dim(hs_refl)[1],
              min=5,
              max=100),2)

n_kg


```

## Merge data
```{r MERGE-DATA}

df <- data.frame(N=n_kg,
                 refl=hs_refl)

```


```{r TRAIN-TEST-GROUPS}

dTrain <- gasoline[1:50,]
dTest <- gasoline[51:60,]

# test trait groups with neon data

dTrain <- df[1:50,]
dTest <- df[51:100,]

# indices
iTrain <- c(1:50)
iTest <- c(51:100)

```

```{r PLS-MODEL}

m1 <- plsr(octane ~ NIR, ncomp = 10, data = dTrain, validation = "LOO")

summary(m1)

m1 <- plsr(n_kg[iTrain] ~ I(hs_refl)[iTrain], ncomp = 10, validation = "LOO")

```

