---
title: "Foliar Biomass Model"
author: "Jeff Atkins"
date: "June 24, 2016"
output: html_document
---
## Foliar biomass model

This model calculates foliar biomass from canopy height based on equations derived from Jenkins et al. 2003 and is trained on data from Ordway-Swisher Biological Station in Hawthorn, FL.

```{r library-import, echo = FALSE, message = FALSE}

library(ggplot2)
library(dplyr)
source("scripts/functions.R")
```

Diameter-at-breast-height (dbh) is calculated from ground-derived site-specific, and "group" specific canopy height equations in a function that calculates dbh. "Group" is defined here as evergreen or deciduous. The dominant species of this time at OSBS are Long-leaf pine and Turkey Oak. 

```{r dbh-calculation}
# Import OSBS data
osbs.dbh <- read.csv("supplemental_data/sarah_osbs_data.csv")

# calculate dbh from ground 
osbs.dbh$calc.dbh <- calc_dbh(osbs.dbh$ht_m, osbs.dbh$group)

```

## DBH error estimation

Let's look at how our calculated dbh compares to our measured dbh.

```{r dbh-error-estimate, message = FALSE}


# subset to pinus palustrus
pine <- subset(osbs.dbh, group == "e")
oak <- subset(osbs.dbh, group == "d")

lm.pine <- lm(dbh_cm ~ calc.dbh, data = pine)
lm.oak <- lm(dbh_cm ~ calc.dbh, data = oak)

# plotting for rational check
ggplot(osbs.dbh, aes(x = calc.dbh, y = dbh_cm, color =group))+
     geom_point()+
     geom_smooth(method = lm, se = FALSE)+
     scale_color_discrete(name="",
                         breaks=c("d", "e"),
                         labels=c("Deciduous", "Coniferious"))+
     ylab("Measured DBH (cm)")+
     xlab("Estimated DBH (cm)")

summary(lm.pine)$adj.r.squared
summary(lm.oak)$adj.r.squared



```