---
title: "func-div-spec-div"
author: "Catherine Hulshof DLP"
date: "June 23, 2016"
output: html_document
---

## Load libraries

```{r load-libraries, eval=FALSE }

library (ggplot2)
library(FD)
library(plyr)

```

## Read in raw vegetation and trait data

```{r read-data }

raw_str <- read.csv("../NEONdata/D03-Florida/OSBS/2014/insitu/veg_structure/D03_2014_OSBS_vegStr.csv")
raw_chem <- read.csv("../NEONdata/D03-Florida/OSBS/2014/insitu/veg_chemistry/D03_2014_OSBS_foliarChem.csv")

```

## Clean up trait data

```{r house-keeping-traits }

# Calculate a new column for SLA and create a single column for scientific name

raw_chem$sla <- 1 / raw_chem$mass_per_area
raw_chem$genus_species <- do.call(paste, c(raw_chem[c("genus", "species")], sep = "_")) 
#names(raw_chem)

```

## Reshape trait data

```{r reshape-trait-matrix, eval = FALSE }

# This creates a species x trait matrix by averaging each trait value for each species

trait.matrix=ddply(raw_chem,~genus_species,summarise,sla=mean(sla,na.rm=TRUE),fifteenN=mean(fifteenN,na.rm=TRUE),thirteenC=mean(thirteenC,na.rm=TRUE),totalN=mean(totalN,na.rm=TRUE),totalC=mean(totalC,na.rm=TRUE))

# Remove the column header from the first column (FD package requirement)

names(trait.matrix)[1]<-c("")

# Write the trait matrix to a .txt file (FD pacakage requires txt file)

write.table(trait.matrix,"trait_matrix.txt",sep="\t")

```

## Clean up veg data

```{r house-keeping-abun }

# Remove the white space in the scientific name and replace it with an underscore

raw_str$scientificname = sub(" ", "_", raw_str$scientificname)

```

## Reshape veg data

```{r reshape-veg-matrix, eval=FALSE }

# Reshape the vegetation data to create a plot x species matrix of abundances

raw_str_summary=with(raw_str, table(plotid, scientificname))

# Create a .txt file (FD package requires txt format)

write.table(raw_str_summary, "abundance_matrix.txt", sep="\t")

```

## Load abundance and trait data

```{r load-tables }

traits <- read.table("trait_matrix.txt",header=T,na.strings = "NA")
abundances <- read.table("abundance_matrix.txt",header=T,na.strings = "NA")

```


## Check the dimension of the trait and abundance file

```{r check-dimensions }

T<-dim(traits)[2]
t2<-dim(traits)[1]
t2
C<-dim(abundances)[1]
c2<-dim(abundances)[2]
c2

```


## Check whether the species names in the trait file match the species names in the abundance file

```{r check-match }

# FD package requires the species in the abundance matrix to be the same and in the same order as the species in the trait matrix

if(dim(abundances)[2]!=dim(traits)[1])stop("error:differentnumberofspeciesin'traits'and'abundances'matrices")

# Determine the mis-matches using the below code:

#mishaps<- colnames(abundances)[which(!(colnames(abundances) %in% rownames (traits)))]
#mishaps
#mishaps2 = rownames(traits)[which(!(rownames(traits) %in% colnames (abundances)))]
#mishaps2

```


## Run the FD function. Warning messages will appear for plots/sites with less than three species. 

```{r run-FD, eval = FALSE }

# see dbFD for documentation on correction factors and number of PCA axes to keep.

FDresults=dbFD(traits,abundances,corr="lingoes",m=3)

```


## Write the results file to a .csv file

```{r write-results, eval = FALSE }

write.csv(FDresults, "FDresults.csv",quote=F)

```

###################
###################

# Testing the PCA analyses on the hdf5 file for florida

```{r load-raster-libraries }

library(raster)
library(rhdf5)
library(rgdal)
library(neonAOP)
library(RStoolbox)

```

# HYPERSPECTRAL FUN TIME

# Identify file of interest

```{r file }
f <- "../../data/NEONDI-2016/NEONdata/D03-Florida/OSBS/2014/spectrometer/reflectance/Subset1NIS1_20140507_150703_atmcor.h5"

```

# ID the projection

```{r define-crs }
# define the CRS definition by EPSG
epsg <- 32617
# create a list of bands
wavelength <- h5read(f,"wavelength")
#bands <- c(1:length(wavelength))
#bands <- c(1:100) # 5 mins
bands <- c(1:10) # 2 mins

# Create the stack
#stack <- create_stack(f, bands = bands, epsg = epsg)

# Stack from Kunxuan
stack1 <- all_h_data

# Perform the PCA
a=rasterPCA(stack, nComp = 3, nSamples = 1600, maskCheck=FALSE, norm = TRUE, spca = TRUE)

```

```{r extract-column-values }
vals <- a$map@data@values
```
bandwidth=estimate_bandwidth(data,method="silverman")

hypervol = hypervolume(vals,bandwidth=estimate_bandwidth(vals,method="silverman"))
hypervol@Volume
